### 2011-02-10 paper/results.tex
shrinking figs

\acmFig{hnResults}{1}{Average fitness ($\pm $ SE) of
  the highest performing individual in the population for each generation of HyperNEAT runs. The fitness of many high-performing HyperNEAT gaits were halved if the gait overly stressed the motors (see text), meaning that HyperNEAT's true performance without this penalty would be much higher.}

@@

\acmFig{neat_110115_211410_00000_002_filt_zoom}{1}{Example of one
  particular high-performance gait produced by HyperNEAT showing
  commands for each of nine motors.  Note the complexity of the motion
  pattern. Such patterns were not possible with the parameterized
  SineModel5, nor would they likely be contrived by a human designing
  a different low-dimensional parameterized motion model.}

>>>>

\acmFig{hnResults}{.8}{Average fitness ($\pm $ SE) of the highest
  performing individual in the population for each generation of
  HyperNEAT runs. The fitness of many high-performing HyperNEAT gaits
  were halved if the gait overly stressed the motors (see text),
  meaning that HyperNEAT's true performance without this penalty would
  be much higher.}

@@

\acmFig{neat_110115_211410_00000_002_filt_zoom}{.8}{Example of one
  high-performance gait produced by HyperNEAT showing
  commands for each of nine motors.  Note the complexity of the motion
  pattern. Such patterns were not possible with the parameterized
  SineModel5, nor would they likely be contrived by a human designing
  a different low-dimensional parameterized motion model.}
